\chapter{Authority, Rules, and Regulations}
\section{Source of Power} All power under these bylaws is derived directly from the University of Michigan's All Campus Constitution (amended and revised, March 2009), Article 1 (Student Governments on Campus), Section 2 (Governments), Section 3 (Democratically Constituted Governments), and the Compiled Code of the Central Student Government.

\section{Definitions} As referenced in these Bylaws, the following terms shall have meaning as defined in this section.
\begin{enumsubsection}
\itemnotoc ``All-Campus Constitution" or ``Constitution" shall refer to the All Campus Constitution as maintained by the Central Student Government 
\itemnotoc ``Rackham Graduate Student Government," or ``Rackham Student Government," or ``RSG," shall refer to the University of Michigan Horace 
H. Rackham School of Graduate Studies student government established by the Constitution. 
\itemnotoc ``CSG" or ``Central Student Government" shall refer to the University of Michigan Board of Regents recognized central student government. 
\itemnotoc ``Rackham" shall refer to the University of Michigan Horace H. Rackham School of Graduate Studies. 
\itemnotoc ``University'' shall refer to the University of Michigan. 
\itemnotoc ``Campus" shall refer to the Ann Arbor campus of the University, to the exclusion of the Flint and Dearborn campuses. 
\itemnotoc ``Student organization" shall refer to student-led groups recognized by the University's Student Organization Account Services department (hereinafter referred to as ``SOAS").
\itemnotoc ``Bylaws" shall refer to this document. 
\itemnotoc ``Graduate Student" or ``Student" shall refer to students currently enrolled in Rackham, or are currently enrolled for the following academic semester in Rackham. 
\itemnotoc ``Student Body" or ``Students" shall refer to the students currently enrolled in the Horace H. Rackham School of Graduate Studies within a given 
academic year.
\itemnotoc ``The Board" shall refer to the legislative branch of the Rackham Student Government, consisting of all currently elected RSG representatives as well as the Student Body President, Vice President, and Treasurer.
\itemnotoc ``Authorized signer" shall be the president, vice president, or treasurer of RSG. 

\itemnotoc ``CSG Registered" \url{https://maizepages.umich.edu/}

\itemnotoc ''SAGE'' shall refer to the Student Advocates for Graduate  Education Coalition founded in part by the Rackham Student Government. 
\end{enumsubsection}

\section{Rackham Graduate Student Government} The Rackham Graduate Student
Government shall consist of the Board, the executives, and the Board's 
committees: the budgetary committee, the academic affairs committee, the 
elections committee, the student life committee, and the legislative affairs 
committee. RSG shall be the only recognized graduate student government by and within the Rackham Graduate School, the Central Student Government (CSG), and the University. 

\section{Amendments to the Bylaws}
\begin{enumsubsection}
\itemnotoc Any amendment to the Bylaws must be presented to the Board 7 days 
before its first reading. A second reading may take place no sooner than 
6 days after the first reading. 
\itemnotoc An amendment to the Bylaws shall not be considered by the Board unless 
both the standing Bylaw and the proposed Bylaw are presented together  to all members of the board at a RSG general meeting where a 
vote on the proposal is scheduled by the President. 
\itemnotoc An amendment to the Bylaws shall not be considered by the Board if the 
amendment creates a conflict within the Bylaws or a conflict between the 
bylaws and the Constitution. Such a conflict may be raised as a point of 
order by any voting member of the Board. Should a conflict be detected 
following a successful vote by the Board, the President will veto the 
resolution and thus declare it void. 
\itemnotoc Amendments will be adopted with a two-thirds majority vote of the Board 
present and voting at the 2nd reading. Amendments are in effect 14 days 
after a passing vote unless otherwise noted in the amendment, with the 
exception of changes to student fees.
\itemnotoc Any amendment that shall modify student fees must be approved by 
Student body-wide, majority vote during either a scheduled fall or winter 
seat election. Fee adjustments approved by the student body will be presented by the President to the Board of Regents of the University of 
Michigan for their approval. Amendments and their corresponding roll-call votes must be recorded in RSG 
meeting's official minutes.
\end{enumsubsection}
\section{Availability of the Bylaws} The Bylaws must be posted on the RSG website.
Electronic copies must be made available to any member of the student body 
upon request.

\section{Conflicts} 
\begin{enumsubsection}
\itemnotoc Any conflict or ambiguity arising between the Bylaws and the 
Constitution shall be resolved in favor of the Constitution. 
\itemnotoc Any conflict or ambiguity arising between the Bylaws and any other 
student government code (including CSG) shall be resolved by the Central 
Student Judiciary on a case by case basis. 
\end{enumsubsection}