\chapter{Directors}
Directors. The following positions are appointed by the President and confirmed 
by the Board for a set term, as provided for by the President. Directors report 
directly to the Executive Board, under the general supervision of the Vice President.
All actions made by the directors contained in this article of the bylaws may be 
vetoed by a majority vote of the executive board or a 2/3rds majority of the Board 
unless otherwise noted.
\section{Events Director} The Events Director shall:
\begin{enumsubsection}
\itemnotoc Be responsible for event calendaring, ensuring that RSG's calendar of 
sponsored events is manageable given the number of seated 
representatives, as well as other external time commitments, including 
federal holidays and academic breaks. 
\itemnotoc Be responsible for event planning, by developing a process for committee 
chairs and representatives to develop their events and to present them for 
approval to the RSG board in a timely manner. This process should be 
developed in concert with the Treasurer and the Vice President who will 
have oversight respectively of the financial and communications aspects 
of the proposed events. Once approved by the executive board, the Events Director will meet with each of RSG's committees to implement the 
new process. 
\itemnotoc Be responsible for coordinating and responding to requests from student 
groups to co-host events, whether in person or by email. 
\itemnotoc Be responsible for compiling and calendaring a list of events to be held at 
the beginning of each semester and present this document to the RSG 
Board by the second meeting of the semester.
\itemnotoc Review all RSG sponsored events within 14 calendar days of an RSG 
sponsored event's conclusion. The Events Director will work with the 
event's planner(s) to construct a written report to the executives and the 
Board of the event which will, at a minimum, contain the following:
\begin{enumsubsubsection}
\itemnotoc A detailed `How To' guide for future chairs or representatives on how 
to hold the event.
\itemnotoc A detailed financial accounting showing both what was budgeted and 
what was actually spent.
\itemnotoc Recommendations as to what went well and what could be improved 
upon should the event be held again.
\itemnotoc Recommendations as to if the event should be hosted again by RSG 
or if there is a more appropriate host. 
\end{enumsubsubsection}
\itemnotoc Be an ex-officio co-chair of the following RSG Committees: Academic 
Affairs, Community Outreach and Social Action, Legislative Affairs and 
Student Life. 
\itemnotoc Have approval authority for all RSG sponsored events. Prior to an event 
being sponsored by RSG, the Events Director will review the proposal and 
will either approve or reject the event plan. Events may be rejected for any 
of the following reasons: incomplete proposal, overlap with other RSG 
events, lack of person power to successfully run the event or any other 
reason approved by another executive. 
\itemnotoc Have the power to modify event plans as necessary to ensure that RSG's 
overarching theme(s) and messages are being delivered.
\itemnotoc Report to the Executive Board.
\itemnotoc Vacancy of this position due to resignation or removal will be filled by the 
President by or at the next regularly scheduled RSG Board meeting. 
\end{enumsubsection}

\section{Elections Director}
\begin{enumsubsection}
\item{Eligibility:} The election director shall be a currently enrolled
University student. The director may run for office during their . The
director should, however, be a current Board member who is not up for
reelection.
\item{Appointment:} The President shall appoint the election director no later
than 39 days in advance of any general election.
\item{Salary:} If the Elections Director is not an RSG board member, a salary
of \$300 shall be paid for services rendered. Under extraordinary
circumstances, the Board, with the recommendation of the Elections
Committee, the Treasurer, and the President may approve a salary bonus
for the ED of up to a maximum of \$200. All monies will be paid upon
successful (as determined by the Board) completion of a given election
cycle.
\item{Duties:} The Election Director Shall:
\begin{enumsubsubsection}
\itemnotoc Report weekly to the president with updates on candidates and
election progress.
\itemnotoc Report the current status of the elections including preparations,
advertising, candidate applications, and the like to the Board at
least once a week upon his/her confirmation by the Board and
until the election is completed, as determined by the President.
\itemnotoc Work with the Elections Committee to advertise the election to
the student body including the ability to run for any open Board
positions as encouraging maximum voter turnout.
\itemnotoc Consult the Office of the Registrar to verify current enrollment
numbers to determine the list of elligbile voters and candidates.
Once a year, this list should be used to apportion representative
seats to the four Rackham divisions.
\itemnotoc Email all eligible graduate students to seek candidates for
representative and executive seats open in the election. This
email should be sent multiple times and the first such email
should be sent no later than 3 weeks prior to the start of the
election.
\itemnotoc No later than 5 p.m. 5 days prior to the start of the election,
candidates must, via email to the ED, indicate their intention to
run. The ED shall consult the Office of the Registrar to verify
current enrollment status and Divisional membership of
candidates.
\itemnotoc Collect all candidate names and uniqnames and will submit
them to the voting website no later than 3 days prior to the
election, at which point a sample official ballot will be posted for
public viewing.
\itemnotoc Be available during the full voting period and answer all
questions received from candidates and members of the Board.
When answered electronically, the elections committee should
be carbon copied on all responses.
\itemnotoc Notify the Board and all candidates of election results no later
than 5 business days after vote counts have been completed.
These results will be posted on the RSG website within 24
hours of notice to the Board being presented.
\itemnotoc Award seats on the RSG Board to the candidates that receive
the highest vote counts. No candidate shall win a seat if he
receives less than 2 eligible votes.
\itemnotoc Ensure that in the event of a tie for a seat, the candidates will
present themselves at the following RSG Board meeting. The
Board will break the type with a majority vote.
\end{enumsubsubsection}
\item{Removal:} The Executive Board may remove the ED for failure to
perform duties, as determined by a majority vote. Should the ED be
removed, any promised salary shall be forfeited. The President will then
appoint a new election director. Should the ED be removed from office
within two weeks of the election, the President or his designee will fulfill
the remaining roles of the Election Director without financial
compensation. The treasurer will reallocate any forfeited salary
accordingly.
\end{enumsubsection}