
\chapter{Membership Rights and Responsibilities} 

\section{RSG Board} The RSG Board shall serve as the legislative branch of the graduate 
student government. The Board shall be chaired by the President and vice-chaired by the Vice-President. All elected representatives in good standing shall have a vote on the Board. The Board shall consider issues of import to the graduate student body and shall offer its input and directives as it sees fit.\\[1cm]
Membership
\begin{enumsubsection}
\itemnotoc Elected Members 
\begin{enumsubsubsection}
\itemnotoc Elected Members are all Board members who have been elected by the 
student body during a regular or special election or nominated by the 
President and confirmed by the Board to fill a vacancy. 
\itemnotoc Elected Members include the president, vice president, and the treasurer. 
\itemnotoc Only Elected Members may vote on official business during Board 
meetings.
\itemnotoc Each Elected Member must be a member of at least one RSG committee as defined in these bylaws. Failure to maintain active committee membership shall be cause for the President to vacate a representative's seat. 
\itemnotoc Each Elected Member must plan, execute, or attend at least two non-meeting RSG events each academic term (fall, winter, and 
spring/summer). Failure to plan, execute, or attend at least two non-meeting RSG events per term shall be cause for the President to vacate a 
representative's seat.

\end{enumsubsubsection}
\itemnotoc Associate Members
\begin{enumsubsubsection}
\itemnotoc Associate Members are all non-elected members who show a continued 
interest in RSG proceedings. 
\begin{enumerate}
\itemnotoc Individuals may become an RSG Associate Member by attending 3 
consecutive Board meetings or by attending 3 consecutive committee meetings. 
\end{enumerate}
\itemnotoc An Associate Member may only vote as a member of an RSG committee. 
\itemnotoc Associate Members may participate in Board discussions and debates. 
\itemnotoc Associate Membership shall expire at the next regularly scheduled 
election as defined in the All Campus Constitution. 
\itemnotoc Associate Members are limited to a single term. Exceptions must be 
requested in writing and approved by the Board. 
\end{enumsubsubsection}
\itemnotoc Appointed Members
\begin{enumsubsection}
\itemnotoc Appointed members are all non-elected members of RSG that have been 
jointly nominated by the President or Vice President and confirmed by a 
majority vote of the Board to serve in a specific leadership role for RSG. 
\itemnotoc With the exception of the RSG Treasurer, appointed Members will not be 
given a vote on the Board. 
\itemnotoc The President and Vice President may notify members of the Graduate 
Student Body of any vacancy in an appointed position. 
\end{enumsubsection}
\itemnotoc Student Body
\begin{enumsubsubsection}
\itemnotoc Members of the student body not included in sections a, b, or c above 
shall be allowed and encouraged to attend RSG Board and committee 
meetings and to provide information to the Board and its committees 
when requested. These members will not be allowed to participate in 
RSG debates or discussions without the permission of an Elected 
Member. 


\end{enumsubsubsection}
\end{enumsubsection}

\section{Board Obligations}
\begin{enumsubsection}
\itemnotoc Attendance \hl{at Board Meetings}: All RSG members are required to attend general meetings. 
After the accumulations of three (3) unexcused absences, the member is 
immediately recalled. \st{Elected Members must also attend a minimum of two RSG sponosred events each semester.}

\itemnotoc \hl{Elected Members must  attend a minimum of two RSG sponsored events each semester.} \hl{Each Elected Member must plan, execute, or attend at least two non-meeting RSG events each academic term (fall, winter, and 
spring/summer). Failure to plan, execute, or attend at least two non-meeting RSG events per term shall be cause for the President to vacate a 
representative's seat.}

\itemnotoc \hl{Attendance at Committee Meetings: All RSG members are required to actively participate in at least one RSG committee. After the accumulation of three (3) unexcused absenses for a given committee, the President will vacate the members' seat.} 


\itemnotoc Excused absence: Any RSG member may receive an excused absence 
from the president provided permission is requested at least 48 hours prior 
to the \st{general} meeting, or within five (5) days subsequent to the absence for reasons deemed appropriate by the president.
\end{enumsubsection}
\section{Operating Procedures}
\begin{enumsubsection}
\itemnotoc Board meetings shall be held weekly during the academic year 
(September--April) and bi-weekly during the summer months. Board 
meeting dates shall be determined by the President prior to the start 
of a term after consulting with the membership of the board.
\itemnotoc \st{No funds may be appropriated by the RSG board to purchase food or 
beverages for RSG members in conjunction with regularly scheduled 
board meetings.}  \hl{Funds may be appropriated by the RSG board to purchase food or beverage for  present RSG members and visitors in conjunction with regularly scheduled, public board meeting on campus, but those funds shall not exceed \$500 per semester.}

\itemnotoc The Board's Agenda will generally include the following items:
\begin{enumsubsubsection}
\itemnotoc Call to Order
\itemnotoc Approval of Agenda
\itemnotoc Approval of Previous Minutes
\itemnotoc Officer Reports
\itemnotoc Director Reports
\itemnotoc Guest Speakers / Discussion
\itemnotoc Funding Request Appeals
\itemnotoc Committee Announcements
\itemnotoc Old Business
\itemnotoc New Business
\itemnotoc Open Discussion
\itemnotoc Adjournment
\end{enumsubsubsection}
\itemnotoc All Board agendas and their supporting documents will be published 
on the RSG Website in a timely manner.
\itemnotoc The Board may adopt additional operating procedures on a term-by-term basis. All such operating procedures shall expire at the end of 
the term in which they were adopted. Operating procedures may be 
adopted by a super-majority vote of the Board at any point.
\itemnotoc{Quorum:} Quorum shall consist of half of all non-vacant voting seats,
rounded up. 
\itemnotoc{Roll call:} Each general meeting shall commence with a roll call 
attendance conducted by the Vice President. This attendance report 
will be included in the meeting's minutes. 
\itemnotoc{Minutes:} Minutes shall be approved electronically or at the next 
General Board meeting. Minutes shall be posted on the RSG website 
(by the Vice President) for all Board members at least 72 hours in 
advance of the next General Board meeting. 
\itemnotoc In accordance with the Constitution, no RSG member shall receive 
monetary compensation from RSG for services rendered.
\itemnotoc Board meetings shall be open to the Student body.
\end{enumsubsection}