\chapter{Board Elections}
\section{Elections} RSG general elections shall be held in November and March on 
dates determined by CSG. The Board may, by a simple majority vote, move the 
date of the elections within the prescribed months. The Board may also vote to 
extend the length of the elections by a simple majority vote. RSG's elections
including candidacy eligibility and timelines shall be subject soley to the provisions contained in these bylaws.

\section{Board Composition} The Board shall consist of currently enrolled Students 
as follows:
\begin{enumsubsection}
\itemnotoc Representation for the Board shall be divided among the four major 
Divisions defined by Rackham: 
\begin{enumsubsubsection}
\itemnotoc Biological and Health Sciences 
\itemnotoc Physical Sciences and Engineering 
\itemnotoc Social and Behavioral Sciences 
\itemnotoc Humanities and the Arts 
\end{enumsubsubsection}
\itemnotoc There shall be one representative for each 400 Students or major fraction 
thereof presently enrolled in each of the Divisions. A major fraction thereof 
shall mean that the remainder is greater than 200 Students after the number 
of Students in the Division is divided by 400. Each Division must receive at 
least one representative, regardless of size.
\begin{enumsubsubsection}
\itemnotoc The basis for deciding a Student's appropriate Division by his/her 
current area of study for the purposes of election shall be 
determined by Rackham. Current Division listings, as of March 1, 
2012 are as follows: 
\begin{description}
\item{Division I - Biological and Health Sciences} \\
Acute Care Nursing\\
Bioinformatics\\
Biological Chemistry\\
Biostatistics\\
Cancer Biology\\
Cell and Developmental Biology\\
Cellular and Molecular Biology\\
Cellular Biotechnology\\
Chemical Biology\\
Clinical Research\\
Clinical Research Des and Statistical Analysis\\
Community Health Nursing\\
Dental Hygiene\\
Ecology and Evolutionary Biology\\
Endodontics\\
Environmental Health Sciences\\
Environmental Justice\\
Epidemiological Science\\
Epidemiology\\
Genetic Counseling\\
Gerontological Nursing \\
Health and Health Care Research\\
Human Genetics\\
Immunology\\
Industrial Ecology\\
Industrial Health\\
Kinesiology\\
Landscape Architecture\\
Medical Scientist Training Practice\\
Medical Surgical Nursing\\
Medicinal Chemistry\\
Microbiology and Immunology\\
Molecular and Cellular Pathology\\
Molecular and Integrative Physiology\\
Molecular, Cellular and Developmental Biology\\
Natural Resources and Environment\\
Neuroscience\\
Nursing\\
Nursing Business and Health Systems\\
Nutritional Science\\
Oral and Maxillofacial Pathology\\
Oral Health Sciences\\
Orthodontics\\
Parent-Child Nursing\\
Pediatric Dentistry\\
Periodontics\\
Pharmaceutical Sciences\\
Pharmacology\\
Physiology\\
Program in Biomedical Sciences\\
Prosthodontics\\
Psychiatric Mental Health Nursing\\
Restorative Dentistry\\
Social and Administrative Sciences\\
Spatial Analysis\\
Toxicology
\item{Division II - Physical Sciences and Engineering}\\
Aerospace Engineering\\
Aerospace Science\\
Applied and Interdisciplinary Mathematics\\
Applied Physics\\
Applied Statistics\\
Astronomy and Astrophysics\\
Atmospheric and Space Science\\
Atmospheric, Oceanic and Space Sciences\\
Biomedical Engineering\\
Biophysics\\
Chemical Engineering\\
Chemistry\\
Civil Engineering\\
Complex Systems\\
Computer Science and Engineering\\
Construction Engineering and Management\\
Design Science\\
Earth and Environmental Sciences\\
Electrical Engineering\\
Electrical Engineering-Systems\\
Environmental Engineering\\
Financial Engineering\\
Geology\\
Industrial and Operations Engineering\\
Macromolecular Science and Engineering\\
Materials Science and Engineering\\
Mathematics\\
Mechanical Engineering\\
Naval Architecture and Marine Engineering\\
Nuclear Engineering and Radiological Sciences\\
Nuclear Science\\
Physics\\
Plasma Science and Engineering\\
Science, Technology and Public Policy\\
Science, Technology, and Society\\
Scientific Computing\\
Space and Planetary Physics\\
Statistics
\item{Division III- Social and Behavioral Sciences}\\
Anthropology\\
Anthropology and History\\
Applied Economics\\
Asian Studies: China\\
Asian Studies: Japan\\
Business Administration\\
Cognitive Science and Cognitive Neuroscience\\
Communication\\
Culture and Cognition\\
Economics Education\\
Education and Psychology\\
Educational Studies\\
Greek and Roman History\\
Health Behavior and Health Education\\
Health Service Organizations and Policy\\
Health Services Research\\
Higher Education\\
History\\
History and Women's Studies\\
Information\\
Latin America and Caribbean Studies\\
Lesbian/Gay/Bisexual/Transgender Queer Studies\\
Modern Middle Eastern and North African Studies\\
Political Science\\
Psychology\\
Psychology \& Women's Studies\\
Public Administration\\
Public Policy\\
Public Policy and Economics\\
Public Policy and Political Science\\
Public Policy and Sociology\\
Real Estate Development\\
Russian and East European Studies\\
Russian, East European and Eurasian Studies\\
Social Work and Social Science\\
Sociology\\
South Asian Studies\\
Southeast Asian Studies\\
Survey Methodology\\
Urban and Regional Planning\\
Urban, Technological, and Environmental Planning\\
Women's Studies and Sociology\\
\item{Division IV - Humanities and the Arts}\\
African American Diasporic Studies\\
African Studies\\
Afroamerican and African Studies\\
American Culture\\
Arabic Studies\\
Architecture\\
Art\\
Asian Languages and Cultures\\
Classical Art and Archaeology \\
Classical Studies\\
Classical Studies-Greek\\
Classical Studies-Latin\\
Comparative Literature\\
Creative Writing\\
Dance\\
English \& Women's Studies\\
English and Education\\
English Language and Literature\\
Film Studies\\
Germanic Language and Literature\\
History of Art\\
Judaic Studies\\
Linguistics\\
Media Arts\\
Medieval \& Early Modern Studies\\
Museum Studies\\
Music Composition\\
Music Composition and Theory\\
Music Conducting\\
Music Performance\\
Music Theory\\
Music Theory Pedagogy\\
Music: Music Education\\
Music: Musicology\\
Near Eastern Studies\\
Philosophy\\
Romance Language and Literature French\\
Romance Language and Literature Italian\\
Romance Language and Literature Spanish\\
Screen Arts and Cultures\\
Slavic Language and Literature\\
Women's Studies\\
Independent Interdependent Degree Program\\
\end{description}
\end{enumsubsubsection}
\itemnotoc A president, who shall be President of the Graduate Student Body of the 
University of Michigan, along with a vice president, each with full voting 
rights. 
\itemnotoc A treasurer, who shall act as the principal financial officer for RSG and chair 
of the Budgetary Committee, with full voting rights. 
\end{enumsubsection}

\section{Terms}
\begin{enumsubsection}
\itemnotoc Two elections shall be held each year. One shall be held during November, and the other shall be held during March. Officers and Representatives shall 
hold their elected seats for one-year terms. One half of the seats apportioned 
to each division shall be elected in the Fall with the other half being elected in 
the Winter. 
\itemnotoc The President and Vice President of the Graduate Student Body shall be 
elected by the student body on a single ticket during the Winter election. 
\itemnotoc The Treasurer shall be nominated by the President and Vice President 
from and among the current and former RSG membership after the fall 
election has concluded. The treasurer will assume office for a one-year term 
upon confirmation by the new Board. A 2/3 majority of the board, including 
the President and Vice President is required to confirm the treasurer. 
\itemnotoc Each representative's one-year term shall begin with the following 
semester. March electees shall assume office beginning the spring semester. 
November electees shall assume office beginning the winter semester. Upon 
election, and prior to taking office as an elected representative, all 
representatives elect shall be considered associate members. 
\end{enumsubsection}

\section{Filling of Elected Seats}
\begin{enumsubsection}
\itemnotoc For any given Division with multiple vacancies during an election cycle, 
the candidate with the most votes is awarded the first seat. The candidate 
with the second highest vote total receives the second seat, and so forth. 
\itemnotoc In the event of a voting tie between two candidates for one seat, the 
\emph{newly} constituted Board shall vote at the first general Board meeting of the 
new term. In the event of a Board voting tie, the votes of representatives of 
the Divisional candidates in question shall decide. In the event of a Divisional 
voting tie, the winner will be determined by the president at the first regularly 
scheduled General Board meeting after the election results were determined. 
\itemnotoc President/vice president: The executive officer positions shall be filled 
together on a single ticket. They shall be elected by general Student body 
vote in the winter term. In the event of a tie, the \emph{newly} constituted Board shall 
vote to determine the winner at the first general meeting of the 
spring/summer term. In the event of a Board voting tie, the treasurer shall 
determine the winner.
\end{enumsubsection}


\section{Petitions, amendments, ballot questions, and referenda} 
\begin{enumsubsection}
\itemnotoc Binding Questions including fee change proposals, bylaw amendments put to the student body or certain other ballot questions may be submitted to the Student body during a general election for campus vote. The Board must approve all such items by majority vote no later than 14 days prior to the general election. Questions to be placed on a general election ballot may not be approved during a first reading.
\itemnotoc Non-binding Questions may be put to the student body through any process as approved by the Board. These may include but are not limited to distribution through an electronic newsletter or in tandem with an election.
\end{enumsubsection}
