\chapter{Executive Officers}
\section{Officers' Powers and Functions}
\begin{enumsubsection}
\item{President:} The president shall: 
\begin{enumsubsubsection}
\itemnotoc Be the chief executive officer of RSG, President of the Graduate Student 
Body, and shall preside at Board meetings with the power to vote. 
\itemnotoc Be authorized to speak on behalf of the RSG Board, its committees, and 
the graduate student body at large.
\itemnotoc Be an authorized signer on all RSG accounts. 
\itemnotoc Be an ex-officio voting member of all RSG committees. 
\itemnotoc Set the time, dates, and frequency for all general Board meetings, set the 
general Board meeting agendas, and chair general Board meetings. 
\itemnotoc Set the time, dates, and frequency for all executive Board meetings, set 
the executive Board meeting agendas, and chair the executive board 
meetings.
\itemnotoc Maintain an updated roster and attendance record for the Board's 
elected and appointed members. 
\itemnotoc Provide voting members with excused absences as deemed necessary 
and appropriate, subject to appeal by the Board. 
\itemnotoc Vacate a representative's seat upon the accumulation of three (3) 
unexcused absences.
\itemnotoc Provide ultimate oversight and management of RSG's paid staff 
members. 
\itemnotoc Create, Charge, and oversee Ad-Hoc committees for specifics projects 
and interests. 
\itemnotoc In the event of either the vice president or treasurer being 
recalled/removed and/or unable to fulfill his/her duties as described in 
these bylaws, nominate a successor. The Board will either confirm or 
reject that nomination. If rejected, the nomination process recommences. 
\itemnotoc Represent the Student body as a voting member of the Rackham 
Executive Board, the governing administrative body of the Graduate 
School. 
\itemnotoc Chair the Legislative Affairs Committee
\itemnotoc Be an ex-officio voting member of all RSG committees
\itemnotoc Be the University of Michigan's official delegate to the Student 
Advocates for Graduate Education.
\itemnotoc Upon leaving office, be responsible for training his/her replacement with 
respect to their new duties during the two weeks following the election 
of a new president. 
\itemnotoc Present a report either orally or in writing to the Board at each meeting 
detailing his/her presidential activities. 
\itemnotoc Appoint members of the graduate student body to university committees as appropriate.
\itemnotoc Appoint members of the graduate student body to vacant seats on the 
Board subject to confirmation by the same. 
\end{enumsubsubsection}
\item{Vice President} The Vice President shall:
\begin{enumsubsubsection}
\itemnotoc Be the chief operating officer of RSG, Vice President of the Graduate 
Student Body, and shall be a member of the Board meetings with the 
power to vote. 
\itemnotoc Be an authorized signer on all RSG accounts. 
\itemnotoc Take minutes at regular Board meetings. 
\itemnotoc Coordinate the activities of RSG committees, including collecting and 
publishing committee meeting minutes. 
\itemnotoc Provide management for RSG's paid staff.
\itemnotoc Provide management for RSG's directors.
\itemnotoc Be an ex-officio voting member of all RSG committees. 
\itemnotoc Present a report either orally or in writing to the Board at each meeting 
detailing his/her vice presidential activities. 
\itemnotoc Be an ex-officio voting member of all RSG committees
\itemnotoc Be an official delegate to the Student Advocates for Graduate Education
\itemnotoc If unable to attend a meeting, submit his/her report in writing to the 
president no later than 48 hours after the meeting. Assume all the 
powers of the president in the event that the president is unable to fulfill 
his/her duties as described in these bylaws and/or is recalled/removed. 
\itemnotoc Manage RSG's communications activities including appointment, 
subject to Board approval, of a newsletter editor, serving as editor for 
all communications emails, and manage RSG's social media presence 
including Facebook and Twitter. 
\itemnotoc When chairing the Board meeting, appoint a temporary secretary to 
take minutes from among the present Board members if the treasurer is unavailable. If the vice president assumes chairing duties, the 
treasurer shall take the minutes. 
\itemnotoc Upon leaving office, be responsible for training his/her replacement 
with respect to their new duties during the two weeks following the 
election of a new vice president. 
\end{enumsubsubsection}
\item{Treasurer:} The Treasurer shall:
\begin{enumsubsubsection}
\itemnotoc Be the chief financial officer of RSG with oversight authority of all RSG 
accounts and financial transactions.
\itemnotoc Be an authorized signer on all RSG accounts. 
\itemnotoc Chair the Budgetary Committee
\itemnotoc Be an ex-officio voting member of all RSG committees
\itemnotoc Recommend to the Board a salary, consistent with the bylaws, for all RSG 
paid staff members.
\itemnotoc Prepare a budget with the advice and consent of the President by the 3\textsuperscript{rd} 
Board meeting of each semester for adoption. Failure by the Board to 
adopt the treasurer's proposed budget after the 5\textsuperscript{th} meeting of a given 
semester shall constitute automatic approval. 
\itemnotoc Disburse funds appropriated by the Budgetary Committee and the Board 
as provided for in the Bylaws. 
\itemnotoc Compile an RSG budget at the beginning of each academic term including 
committee budgets, representative project budgets, executive 
discretionary accounts, and other potential expenses.
\itemnotoc Compile an RSG Funding report at the end of each term. 
\itemnotoc Manage the approved RSG budget.
\itemnotoc Report at every general Board meeting the current state of the RSG 
budget and all RSG accounts, including pending credits and debits. 
\itemnotoc If unable to attend a meeting, submit his/her report in writing to the 
president no later than 48 hours after the meeting. 
\itemnotoc Have the authority to interpret the spirit and intent of funding articles of 
these bylaws and to implement the same subject to approval by the 
President.
\itemnotoc Complete a full funding report at the close of the fall, winter, and 
spring/summer semesters for which s/he was appointed detailing all 
expenditures. This report shall be submitted to the Board and published to 
the Student body. 
\itemnotoc Upon leaving office, be responsible for training his/her replacement with 
respect to their new duties during the two weeks following the election of a 
new treasurer. 
\itemnotoc Present a report either orally or in writing to the Board at each meeting 
detailing his/her Treasurer activities. 
\itemnotoc The treasurer is responsible for producing a detailed Budget for each fall,
winter, and spring/summer term, presented to the Board no later than the 
4\textsuperscript{th} week of the academic term. Budgets shall be approved by a majority 
vote of the Board and shall be posted on the RSG website, and 
hardcopies shall be made available to any interested Student. 
\itemnotoc The Treasurer will produce a detailed spending report at the conclusion of 
each academic term. This report will include all funds budgeted and 
expended as well as all submitted event evaluation forms. The Board will 
review the report and approve it if correct by the 3rd week of the following 
semester. Approved funding reports will be placed on the RSG website 
and made available to any interested Student. 
\end{enumsubsubsection}
\end{enumsubsection}
\section{Officers' Terms} Newly elected officers begin their terms with the commencement of 
the new semester. The president and vice president shall assume their 
duties on the first day of classes of the spring semester. The treasurer shall 
assume his/her duties on January 1\textsuperscript{st}.