\chapter{Funding}
\section{Funding Guidelines}\label{sec:fun_guid}
\begin{enumsubsection}
\itemnotoc The Board and its Budgetary Committee will consider funding requests 
student organizations. Requests for event funding will be reviewed on 
a first-come, first-served basis. Groups may be requested to make a 
presentation to the Budgetary Committee, at the discretion of the 
treasurer.
\itemnotoc The Budgetary Committee will not consider retroactive funding 
requests.
\itemnotoc \label{sec:bud_timeline}The Budgetary Committee will not consider funding requests 
submitted fewer than twenty one (21) days prior to an event. This 
restriction may be waived by the Treasurer on a case-by-case basis. 
\itemnotoc \label{sec:bud_realloc}All monies appropriated for a funding request will be for specific items 
originally listed in a submitted budget. Where budget items are 
originally approved but have less or no expense actually incurred, 
excess appropriated funds will be forfeited. Funds cannot be 
reallocated to budget items not previously approved by the Board. The 
requesting organization may request a reallocation from the Treasurer 
within the appropriated monies. Re-allocations will be reported to the 
Budgetary Committee and to the Board and should only be approved 
in the spirit of the committee's original funding rationale.
\itemnotoc The guidelines contained in the following four clauses will be used by 
the RSG Budgetary Committee and the Board in making decisions 
about funding requests. Each request will ultimately be considered on 
its individual merits. 
\itemnotoc The following are likely to be funded: 
\begin{enumsubsubsection}
%\itemnotoc Academic events
\itemnotoc Cultural events 
\itemnotoc Proposals that are well written with a detailed budget, including 
expenses and expected/secured income 
\itemnotoc Events which are public and held on campus 
\itemnotoc Community service events involving or benefiting graduate students 
\itemnotoc Projects that may need start-up funds but which will become self-sustaining in a short period of time 
\itemnotoc Events that involve more than 100 graduate students and/or have 
at least 25\% graduate student participation 
\itemnotoc Programs designed to enhance quality of life for the Student body.
\end{enumsubsubsection}
\itemnotoc The following are not likely to be funded:
\begin{enumsubsubsection}
\itemnotoc Parties 
\itemnotoc Events not open or easily accessible to the entire UM community 
\itemnotoc Publications which do not positively impact the UM community 
\itemnotoc Events that, \st{in our judgment}, should be receiving funds from some 
other obvious, appropriate source 
\itemnotoc Club sports 
\itemnotoc Proposals from social fraternities or sororities 
\itemnotoc Proposals from lobbyists 
\itemnotoc Capital goods 
\itemnotoc Activities exclusive to the membership of one organization 
\itemnotoc Film and photo development/photographers/videographers 
\itemnotoc Loans 
\itemnotoc Political lobbying
\end{enumsubsubsection}
\itemnotoc The following may require additional information prior to consideration:
\begin{enumsubsubsection}
\itemnotoc Honoraria 
\itemnotoc Travel 
\itemnotoc Requests from the Central Student Government. 
\itemnotoc Guest Speakers (biographies, prior speaking engagements)
\end{enumsubsubsection}
\itemnotoc The following will not be funded: 
\begin{enumsubsubsection}
\itemnotoc Alcohol 
\itemnotoc Drugs 
\itemnotoc Medication 
\itemnotoc Charitable contributions 
\itemnotoc Projects / Activities in which students are receiving course credit for 
completion
\itemnotoc Human resources (coaches, secretaries, employees) 
\itemnotoc Late fees/penalties of any type 
\itemnotoc Proposals with non-itemized budgets 
\itemnotoc Plaques/trophies/prizes 
\itemnotoc Scholarships/stipends/awards 
\itemnotoc Events intended for participation by the entire graduate student 
body if that event is scheduled for a day that is identified as a 
major holiday on the calendar of University sanctioned holidays.
\end{enumsubsubsection}
\end{enumsubsection}
\section{Organization Funding Reports}
\begin{enumsubsection}
\itemnotoc Upon a Board or Budgetary Committee decision to fund a group, the treasurer will send an email to the group's contact person that designates the date – 30 days after the event takes place – by which a report and receipts are due. A detailed event report, provided by the treasurer in that email, must include the number of students in attendance, the percentage of graduate students attending, a summary of how the event went, as well as a financial breakdown. Organizations failing to meet this deadline will forfeit any appropriated funds and will be excluded from requesting/receiving RSG funding until at least the end of the current semester pending any appeal to the Board. This exclusion may be extended by a majority vote of the Budgetary Committee. Under circumstances beyond an organization's control, the treasurer may extend this deadline provided groups send timely and reasonable requests for such an extension. 
\itemnotoc The funded organization must provide itemized receipts verifying that the allocated fund were used appropriately and in accordance with the budgetary committee's allocation decision as well as any approved reallocation requests. In the case where an itemized receipt isn't available, proof must be provided and is subject to the Treasurer's discretion. 
\itemnotoc Per Bylaw \ref{sec:bud_realloc}, items in funding reports not approved by the Budgetary Committee or approved by the Treasurer in a reallocation request will not be reimbursed. 
\end{enumsubsection}