\chapter{Recall and Appointment Power}
\section{Recall}For conduct deemed inappropriate by members of the Board, a recall 
vote may be initiated against another representative and/or officer. A board 
member shall be considered recalled after a seconded motion and 3/4 majority vote 
of the Board.

\section{Appointments to Vacated Seats}
\begin{enumsubsection}
\item{Board members}: In the event of a vacancy due to recall, election to an 
officer position, graduation, resignation, or any other reason, the President
may canvass the Student body via email to invite interested Students to serve 
as Representatives for the remainder of the term. Any Associate (non-voting, 
but regularly participating) Member in the same Division as the vacated seat 
shall be included in the President's nomination considerations. The President 
shall nominate a graduate student to fill the vacancy. If the nominated student 
is enrolled in the same division as the vacant seat, a simple majority vote of 
the Board shall be required to confirm the nomination. In the event that the 
nominated student is enrolled in a different Rackham division than the vacant 
seat, a 2/3rds majority vote shall be required to confirm the nomination. The 
appointed representative shall only serve out the remainder of the previous 
representative's term. 
\item{Executive Officers}:
\begin{enumsubsubsection}
\item{President}: If the president cannot fulfill his/her duties as described in 
these bylaws or is recalled, the vice president shall assume 
presidential duties. 
\item{Vice President}: If the vice president cannot fulfill his/her duties as 
described in these bylaws or is recalled, the president shall 
nominate a successor. The Board will either confirm or reject that 
nomination. If rejected, the nomination process recommences. 
\item{Treasurer}: If the treasurer cannot fulfill his/her duties as described 
in these bylaws or is recalled, the president and vice president 
shall nominate a successor. The Board will either confirm or 
reject that nomination. If rejected, the nomination process 
recommences. 
\end{enumsubsubsection}
\end{enumsubsection}