\chapter{Resolutions}
\section{Resolution Types}
\begin{enumsubsection}
\itemnotoc A sense of the Board (SB) shall be an official statement on behalf of the 
student body as articulated by the Board. 
\itemnotoc A Board Resolution (BR) shall be an official policy declaration of the 
student body as articulated by the Board. Board resolutions shall be 
binding on all officers, members, and committees of RSG for matters 
pertaining to RSG internal business. In the case where the subject of a
BR is external to RSG, The President shall transmit the approved BR to the Dean for her review and approval as well as such other officers, offices, or entities as directed by the resolution or as appropriate.
\end{enumsubsection}
\section{Format}
\begin{enumsubsection}
\itemnotoc Every RSG resolution shall contain the following:
\begin{enumsubsubsection}
\itemnotoc A title.
\itemnotoc A unique resolution number.
\itemnotoc A set of descriptive clauses, explaining the rationale for the 
resolution and providing support for any operative clauses 
contained within the resolution. 
\itemnotoc A minimum of one operative clause directing action in the case of 
a BR or stating an opinion in the case of a SB. 
\begin{enumerate}
\itemnotoc The first operative clause in a BR shall have a format 
``Therefore be it resolved by the Rackham Student 
Government on behalf of the student body of the Horace H. 
Rackham Graduate school that"
\itemnotoc The first operative clause in a SR shall have a format 
``Therefore, on behalf of the student body of the Horace H. 
Rackham Graduate school and articulated by its elected 
representatives, it is the sense of the Board that"
\end{enumerate}
\itemnotoc The signature upon final vote of the Vice President or his/her 
designee to the vote count and that the process to consider a 
resolution as outlined in this article and in Roberts Rules of Order 
was followed. 
\itemnotoc The signature of the President approving or vetoing the final 
passage of the resolution.
\end{enumsubsubsection}
\end{enumsubsection}
\section{Voting}
\begin{enumsubsection}
\itemnotoc All voting members of the Board shall be able to vote on RSG 
Resolutions. 
\itemnotoc The President, when chairing deliberations of a resolution shall only vote 
on the final passage thereof to make or break a tie vote. 
\itemnotoc The Vice President, will retain his/her full vote on the final passage of a 
resolution, regardless of if chairing the Board.
\itemnotoc The Treasurer, will retain his/her full vote on the final passage of a 
resolution, regardless of if chairing the Board. 
\end{enumsubsection}
\section{Student Body Input}
\begin{enumsubsection}
\itemnotoc Upon a motion, second, and majority vote by the Board any resolution 
may be postponed to a time certain to allow for formal input from the 
student body. 
\itemnotoc Unless waved by a 2/3rds majority of the Board, a vote to adopt a BR will 
be out of order unless a public hearing on the BR has been advertised 
and conducted. 
\end{enumsubsection}
\section{Public Hearings}
\begin{enumsubsection}
\itemnotoc Board resolutions serve as official statements of policy and as such 
require input from the student body. 
\itemnotoc Prior to the second reading of a BR, notice shall be posted to the RSG 
website as well as to the student body via each department / program's 
graduate coordinators, and via an email to the graduate student body that 
a resolution shall be coming to a vote. The notice shall include the title of 
the resolution, a short description of the resolution including objective pros 
and cons, and the date / location of the meeting where the Board will 
consider the resolution. 
\end{enumsubsection}
\section{Executive Veto}
\begin{enumsubsection}
\itemnotoc Resolutions not approved by the President within 1 week of passage
by the Board shall be in full force and approved. 
Resolutions vetoed by the President shall be presented to the Board at 
its next regularly scheduled meeting. The resolution shall be 
accompanied by a memo indicating the rationale for the veto. Upon a 
motion, second, and 2/3rds majority vote of the Board, the veto shall be 
overridden and the resolution shall be in full force.
\end{enumsubsection}
\section{Publication}
\begin{enumsubsection}
\itemnotoc Upon the final adoption and approval of a resolution, a signed version of 
shall be posted to the RSG website and included in the Board's minutes. 
\itemnotoc Copies of the approved resolution should also be transmitted to the 
Michigan Daily, the Michigan Voice, CSG, and members of the Student 
Body (upon request). 
\end{enumsubsection}